Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-08 paper/paper.tex
abstract: incorporate Gs comments

\begin{abstract}
The default mode network (DMN) is believed to subserve the human
baseline mental activity.
%
Many research streams converge to its likely role in evolutionarily adaptive
envisioning of mental scenarios to simulate the future.
\suggestremove{The DMN may be dedicated to continuous autobiographical memory retrieval,
generation of hypothetical outcomes,
and reward contingency evaluation when letting the mind go.}
Such functional roles offer explanations of
its highest energy consumption in the brain and
its intimate coupling with conscious awareness
\textbf{(XXX Guillaume: It escaladed quickly.)}.
%
This concept paper proposes a process model \textbf{(XXX Guillaume: It's not clear what a "process model" is for most people?)} that describes
\textit{how} the DMN may actually implement continuous
assessment and prediction of the environment to guide action choices.
DMN function is recast in the mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
We argue that our formal account of DMN function
naturally accommodates \suggestremove{previously} proposed cognitive accounts as special cases and
parsimoneously explains \suggestremove{various} experimental findings in \suggestadd{both} animals and humans.
%
Formal models of the neural computations realized in the DMN
could offer access routes to the statistical regularities
of human predictive behavior \textbf{(XXX Guillaume: Maybe too wordy\ldots)}.
\end{abstract}

>>>>

\begin{abstract}
The default mode network (DMN) is believed to subserve the human
baseline mental activity.
%
Many research streams converge to its likely role in evolutionarily adaptive
envisioning of mental scenarios to simulate the future.
Such functional roles become more likely due to
this brain network's highest energy consumption in the brain and
its intimate coupling with conscious awareness
\textbf{(XXX Guillaume: It escaladed quickly.)}.
%
The present concept paper proposes a process model
in trying to explain \textit{how} the DMN may actually implement continuous
assessment and prediction of the environment to guide action choices.
DMN function is recast in the mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
We argue that our formal account of DMN function
naturally accommodates proposed cognitive accounts as special cases and
parsimoneously explains
experimental findings in animals and humans.
%
Formal process models of the neural implemention
of future predictions probably realized in the DMN
could offer insight into the statistical mechanisms underlying
human behavior.
\end{abstract}
